Tool-driven Revolutions in Archaeological Science

### 2018-12-18 analysis/paper/jcaa-paper.Rmd

The use of R or any other scripting languages enables a major shift in the technical and social dynamics of the research community, as it offers the possibility to share one's code. The sharing of code has been identified in other disciplines as an amplifier of change in methods [@Touchon_McCoy_2016]. It also enables researchers to not just reproduce the work of others, but to also evaluate them according to the scientific method. Thus, the sharing of code may be at the root of an upcoming tool-driven change for archaeology, consistent with what we see desribed in the work of @Galison_1997 [-@Galison_1997]. This change does not take place revolutionary-quick and does not replace older ideas as such (as has been a critique of Kuhn's idea-driven concept of paradigm shift by others [@Meltzer_1979; @Trigger_2006]).

>>>>

The use of R or any other scripting languages enables a major shift in the technical and social dynamics of the research community, as it offers the possibility to share one's code. The sharing of code has been identified in other disciplines as an amplifier of change in methods [@Touchon_McCoy_2016]. It also enables researchers to not just reproduce the work of others, but to also evaluate them according to the scientific method. Thus, the sharing of code may be at the root of an upcoming tool-driven change for archaeology, consistent with what we see desribed in the work of @Galison_1997 [-@Galison_1997]. This change does not take place revolutionary-quick and does not replace older ideas as such (as has been a critique of Kuhn's idea-driven concept of paradigm shift by others [@Meltzer_1979; @Trigger_2006].
